### 2015-09-03 articles_of_association_english_french.tex
fr title changed
Adjusted spacing

\french
	\section*{Articles d'association}

@@

\french
	\subsubsection{Conditions d’adhésion}\stepcounter{art}
	Chaque personne voulant participer et contribuer à l’association peut devenir membre.

@@

@@

\english
	\subsubsection{Voting Rights}\stepcounter{art}
	 «Starter», «Resident» and Executive Committee members have equal voting rights. Passive members have no voting rights.
\french
	\subsubsection{Droit de vote}\stepcounter{art}
	Les membres «Starter», «Resident» et les membres du Comité de Direction ont des droits de votes égaux. Les Membres Passifs n'ont pas de droit de vote.

@@

\english
	\subsubsection{Passive Membership}\stepcounter{art}
	Members observing the associations activities without participating actively fall into the category of a Passive Member. Passive Members pay no membership fee but are also not permitted to access tools, materials or any of the other facilities the association provides. Passive members have no voting rights.

@@

	L’Assemblée Générale sera considérée valide indépendamment du nombre de membres présents. Les décisions de l’Assemblée Générale sont prises en se référant à la majorité des voies. En cas d’égalité, le Président a le vote décisif.

@@

@@

	\begin{enumerate}[(a)]
	\item sponsors
	\item membership fees
	\item donations
	\item events, workshops
	\item sale of goods and services
	\end{enumerate}

@@

	\english
	\subsubsection{Liabilities}\stepcounter{art}
	Only the associations assets can be made liable for debts of the association. Personal liability of the Executive Committee or members is excluded.

	\french
	\subsubsection{Responsabilités}\stepcounter{art}
	Seuls les biens de l’association peuvent être utilisés pour les dettes de l’association. La responsabilité personnelle du Comité de Direction et des membres est exclu.
% =================================

@@

	In particular, the association ensures that at least half of the Executive Committee is comprised of EPFL or UNIL members, the president being registered with EPFL or UNIL and that the associations activities target members of EPFL.

@@

	En particulier, l’association certifie qu’au moins la moitié du Comité de Direction est membre des campus de l’EPFL, que le Président est immatriculé à l’EPFL et que les activités de l’association ciblent les membres de l’EPFL.

@@

	\english
	\subsubsection{Revision of the Articles of Association}\stepcounter{art}
	The present Articles of Association may be altered by the General Assembly if more than half of the members present and liable to vote agree.

>>>>

\french
	\section*{Statuts de l’Association}

@@

\french
	\subsubsection{Conditions d’adhésion}\stepcounter{art}
	Chaque personne voulant participer et contribuer à l’association peut devenir membre.
	\vspace{0.5cm}

@@

	\vspace{0.5cm}

@@

\english
	\subsubsection{Voting Rights}\stepcounter{art}
	 «Starter», «Resident» and Executive Committee members have equal voting rights. Passive members have no voting rights.
	 	\vspace{0.5cm}

\french
	\subsubsection{Droit de vote}\stepcounter{art}
	Les membres «Starter», «Resident» et les membres du Comité de Direction ont des droits de votes égaux. Les Membres Passifs n'ont pas de droit de vote.

@@

\english
	\subsubsection{Passive Membership}\stepcounter{art}
	Members observing the associations activities without participating actively fall into the category of a Passive Member. Passive Members pay no membership fee but are also not permitted to access tools, materials or any of the other facilities the association provides. Passive members have no voting rights.
	\vspace{0.6cm}

@@

	L’Assemblée Générale sera considérée valide indépendamment du nombre de membres présents. Les décisions de l’Assemblée Générale sont prises en se référant à la majorité des voies. En cas d’égalité, le Président a le vote décisif.
	\vspace{1cm}

@@

	\vspace{2cm}

@@

	\begin{enumerate}[(a)]
	\item sponsors
	\item membership fees
	\item donations
	\item events, workshops
	\item sale of goods and services
	\end{enumerate}
	\vspace{0.27cm}

@@

	\english
	\subsubsection{Liabilities}\stepcounter{art}
	Only the associations assets can be made liable for debts of the association. Personal liability of the Executive Committee or members is excluded.
		\vspace{1.5cm}

	\french
	\subsubsection{Responsabilités}\stepcounter{art}
	Seuls les biens de l’association peuvent être utilisés pour les dettes de l’association. La responsabilité personnelle du Comité de Direction et des membres est exclu.
		\vspace{1.5cm}

@@

	In particular, the association ensures that at least half of the Executive Committee is comprised of EPFL or UNIL members, the president being registered with EPFL or UNIL and that the associations activities target members of EPFL. 
			\vspace{2.5cm}

@@

	En particulier, l’association certifie qu’au moins la moitié du Comité de Direction est membre des campus de l’EPFL, que le Président est immatriculé à l’EPFL et que les activités de l’association ciblent les membres de l’EPFL.
			\vspace{2.5cm}

@@

	\english
	\subsubsection{Revision of the Articles of \\ Association}\stepcounter{art}
	The present Articles of Association may be altered by the General Assembly if more than half of the members present and liable to vote agree. 		
	\vspace{0.5cm}
